Refinements for open automata

### 2022-08-18 2021-Refinement/paper/refinementarticle.tex
adding reference

>>>>

\TODO{Simulation: Il y a differentes facons de voir le relation de reffinement entre l'implem et la spec:
\begin{itemize}
\item implem as a conformance of spec:  implem deadlocks less often.
\item implem as a (nondeterminism) reduction of spec:  implem deadlocks less often. Can only used be used for complete specification.
\item implem as an extension of spec. C'est le complement du raffinement par reduction, i.e. Can be used to complete partial specification (implem can exhibit more behaviour than spec).
Our definition of simulation matches the definition given in \cite{EshuisF:2002} Section 3.2 $\implies$ Refinement par extension according to Thm 8 (Section 4)
\end{itemize}
}
